---
title: "R Markdown Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.Loading and Processing data
```{r}
activity <- read.csv("activity.csv")
```

2.What is mean total number of steps taken per day?
```{r}
library(dplyr)
activity1 <- activity %>% group_by(date) %>% summarise(total = sum(steps,na.rm = T))

hist(activity1$total, main = "Histogram of Total Number of Steps Taken Each Day", xlab = "Total Number of Steps Taken Each Day")

mean(activity1$total)

median(activity1$total)
```

3.What is the average daily activity pattern?
```{r}
activity2 <- activity %>% group_by(interval) %>% summarise(average = mean(steps,na.rm = T))

plot(activity2$interval, activity2$average, type = "l",
     main = "Time Series Plot",
     xlab = "5-minute interval",
     ylab = "Average Number of Steps Taken")

activity2[which.max(activity2$average),1]
```

4.Imputing missing values
```{r}
sum(is.na(activity$steps))

activity3 <- activity %>%
             group_by(interval) %>%
             mutate(steps =       
             ifelse(is.na(steps),mean(steps, na.rm = T),steps))

activity4 <- activity3 %>% group_by(date) %>% summarise(total = sum(steps,na.rm = T))

hist(activity4$total, main = "Histogram of Total Number of Steps Taken Each Day", xlab = "Total Number of Steps Taken Each Day")

mean(activity1$total)

median(activity1$total)
```

5.Are there differences in activity patterns between weekdays and weekends?
```{r}
activity3$weekday <- weekdays(as.Date(activity3$date))

activity3$factor <- as.factor(ifelse((activity3$weekday ==       
                           "Saturday" | activity3$weekday ==                                "Sunday"), "Weekend","Weekday"))

activity5 <- activity3 %>% group_by(interval,factor) %>% summarise(average = mean(steps))

library(ggplot2)
qplot(interval, average,data = activity5, 
      facets = .~factor, geom = "line",
     main = "Time Series Plot",
     xlab = "5-minute interval",
     ylab = "Average Number of Steps Taken")
     

